---
title: "Predictive Maintenance For Machine Component Replacement"
author: "Satish Kumar"
date: "17 September 2018"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Clearing the Global Environment
```{r}
rm(list = ls(all=TRUE))
```


```{r}
library("dplyr") # Data munging functions
library("zoo")   # Feature engineering rolling aggregates
library("data.table") # Feature engineering
library("ggplot2") # Graphics
library("scales") # For time formatted axis
library(gbm)
#library("C5.0")

```

##### Setting the current directory path and reading all the source files.

```{r}
setwd("C:\\Users\\SaiRam\\Desktop\\PHD\\phd_dataFinal")
ComponentServiceLog <- read.csv("ComponentServiceLog.csv",header = TRUE)
ComplaintsLog <- read.csv("ComplaintsLog.csv",header = TRUE)
MachinesDetails <- read.csv("MachinesDetails.csv",header = TRUE)
ComponentRepLog <- read.csv("ComponentReplacementLog.csv",header = TRUE)
OperCondData <- read.csv("OperatingConditionsData.csv",header = TRUE)

```

##### Source Files has 4 columns YEAR,MONTH,DAY and Time. Concatenating them to get timestamp. New ColumnName is datetime.

```{r}
OperCondData$datetime <-strptime(paste(paste(as.character(OperCondData$Year),as.character(OperCondData$Month),
                                          as.character(OperCondData$Day),sep='-'),as.character(OperCondData$Time),sep=' '), "%Y-%m-%d %H:%M:%S")
OperCondData$datetime <- as.POSIXct(OperCondData$datetime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")

ComplaintsLog$datetime <-strptime(paste(paste(as.character(ComplaintsLog$Year),as.character(ComplaintsLog$Month),
                                       as.character(ComplaintsLog$Day),sep='-'),as.character(ComplaintsLog$Time),sep=' '), "%Y-%m-%d %H:%M:%S")
ComplaintsLog$datetime <- as.POSIXct(ComplaintsLog$datetime,format="%m/%d/%Y %I:%M:%S %p",tz="UTC")
ComponentServiceLog$datetime <-strptime(paste(paste(as.character(ComponentServiceLog$Year),as.character(ComponentServiceLog$Month),
                                            as.character(ComponentServiceLog$Day),sep='-'),as.character(ComponentServiceLog$Time),sep=' '), "%Y-%m-%d %H:%M:%S")
ComponentServiceLog$datetime <- as.POSIXct(ComponentServiceLog$datetime,format="%m/%d/%Y %I:%M:%S %p",tz="UTC")

ComponentRepLog$datetime <-strptime(paste(paste(as.character(ComponentRepLog$Year),as.character(ComponentRepLog$Month),
                                         as.character(ComponentRepLog$Day),sep='-'),as.character(ComponentRepLog$Time),sep=' '), "%Y-%m-%d %H:%M:%S")
ComponentRepLog$datetime <- as.POSIXct(ComponentRepLog$datetime,format="%m/%d/%Y %I:%M:%S %p", tz="UTC")

```

##### After the new feature datetime is derived,dropping the unwanted columns YEAR,MONTH,DAY and TIME
```{r}
OperCondData$Year <- NULL
OperCondData$Month <- NULL
OperCondData$Day <- NULL
OperCondData$Time <- NULL

ComponentServiceLog$Year <- NULL
ComponentServiceLog$Month <- NULL
ComponentServiceLog$Day <- NULL
ComponentServiceLog$Time <- NULL

ComplaintsLog$Year <- NULL
ComplaintsLog$Month <- NULL
ComplaintsLog$Day <- NULL
ComplaintsLog$Time <- NULL

ComponentRepLog$Year <- NULL
ComponentRepLog$Month <- NULL
ComponentRepLog$Day <- NULL
ComponentRepLog$Time <- NULL

```

##### Basic Statistics of the data
```{r}
print("Total Number of OperCondData records : ")
print(nrow(OperCondData))
print("Total Number of error records : ") 
print(nrow(ComplaintsLog))
print("Total number of ComponentServiceLogenance records : ")
print(nrow(ComponentServiceLog))
print("Total number of MachinesDetails : ")
print(nrow(MachinesDetails))
print("Total number of ComponentRepLog : ") 
print(nrow(ComponentRepLog))
#MachinesDetails[c(1:5, nrow(MachinesDetails)-4:0),]
#ComponentRepLog[c(1:5, nrow(ComponentRepLog)-4:0),]
#summary(MachinesDetails)
#ComponentServiceLog[c(1:5, nrow(ComponentServiceLog)-4:0),]
#ComplaintsLog[c(1:5, nrow(ComplaintsLog)-4:1),]
```

##### Converting the Categorical Variabes to Factors

```{r}
ComplaintsLog$errorID <- as.factor(ComplaintsLog$ErrorID)
ComponentServiceLog$ComponentAttended <- as.factor(ComponentServiceLog$ComponentAttended)
MachinesDetails$model <- as.factor(MachinesDetails$MachineModel)
ComponentRepLog$ComponentReplacement <- as.factor(ComponentRepLog$ComponentReplacement)
```


```{r}
head(OperCondData)
```


##### Plotting using ggplot2

```{r}
theme_set(theme_bw())  # theme for figures
options(repr.plot.width = 8, repr.plot.height = 6)

ggplot(data = OperCondData %>% filter(MachineID %in% c('MID10801','MID10802','MID10803','MID10804'), 
                                   datetime > as.POSIXct("2017-01-01"),
                                   datetime < as.POSIXct("2018-02-01")),
       aes(x = datetime, y = Sensor1, col = factor(MachineID))) +
  geom_line(alpha = 0.5) +
  labs(y = "Sensor1", color = "MachineID") +
  facet_wrap(~MachineID, ncol=1) +
theme(panel.background = element_rect(fill="palegreen1"))


options(repr.plot.width = 5, repr.plot.height = 3)
ggplot(ComplaintsLog, aes(x = errorID)) + 
  geom_bar(fill = "green") + 
  labs(title = "ComplaintsLog by type", x = "Error Types") +
theme(panel.background = element_rect(fill="palegreen1"))

options(repr.plot.width = 6, repr.plot.height = 5)
ggplot(ComplaintsLog %>% filter(MachineID %in% c('MID10801','MID10802','MID10803','MID10804')), 
       aes(x = errorID, fill = factor(MachineID))) + 
  geom_bar(color = "black") + 
  labs(title = "ComplaintsLog Type for MachineID MID10801,MID10802,MID10803,MID10804", x = "error types", fill="MachineID")+
  facet_wrap(~MachineID, ncol = 1)+
theme(panel.background = element_rect(fill="palegreen1"))

options(repr.plot.width = 7, repr.plot.height = 5)
ggplot(ComplaintsLog %>% filter(MachineID %in% c('MID10801','MID10802','MID10803','MID10804')), 
       aes(y = errorID, x = datetime)) + 
  geom_point(color = "black", alpha = 0.5) + 
  labs(title = "MachineID 4 ComplaintsLog", x = "Date")+
theme(panel.background = element_rect(fill="palegreen1"))


options(repr.plot.width = 5, repr.plot.height = 3)
ggplot(ComponentServiceLog, aes(x = ComponentAttended)) + 
  geom_bar(fill= "green") +
  labs(title = "Component Types", x = "component types") +
theme(panel.background = element_rect(fill="palegreen1"))

options(repr.plot.width = 6, repr.plot.height = 8)
ggplot(ComponentServiceLog %>% filter(MachineID %in% c('MID10801','MID10802','MID10803','MID10804')), 
       aes(x = ComponentAttended, fill = factor(MachineID))) + 
  geom_bar(color = "black") +
  labs(title = "Component replacements", x = "component types", fill = "Machine ID")+
  facet_wrap(~MachineID, ncol = 1) +
  theme(panel.background = element_rect(fill="palegreen1"))


options(repr.plot.width = 8, repr.plot.height = 6)
ggplot(MachinesDetails, aes(x = ServicePeriod, fill = model)) + 
  geom_histogram(color = "black") + 
  labs(title = "MachinesDetails", x = "Service Period (years)") +
  facet_wrap(~model) +
  theme(panel.background = element_rect(fill="palegreen1"))


options(repr.plot.width = 5, repr.plot.height = 3)
ggplot(ComponentRepLog, aes(x = ComponentReplacement)) + 
  geom_bar(fill = "green") + 
  labs(title = "Components ComponentReplacement distribution", x = "component type")+
theme(panel.background = element_rect(fill="palegreen1"))

options(repr.plot.width = 6, repr.plot.height = 6)
ggplot(ComponentRepLog %>% filter(MachineID %in% c('MID10801','MID10802','MID10803','MID10804')),
       aes(x = ComponentReplacement, fill = factor(MachineID))) + 
  geom_bar(color = "black") + 
  labs(title = "ComponentReplacement distribution", x = "component type", fill = "MachineID") +
  facet_wrap(~MachineID, ncol=2) +
theme(panel.background = element_rect(fill="palegreen1"))

```
##### Creating 4 Columns Sensor1mean,Sensor2mean,Sensor3mean,Sensor4mean out of available columns . Columns are derived by taking moving means of 3 records for every third record.
```{r}


print("A")
  OperCondDatamean <- OperCondData %>%
  arrange(MachineID, datetime) %>% 
  group_by(MachineID) %>%
  mutate(Sensor1mean = rollapply(Sensor1, width = 3, FUN = median, align = "right", fill = NA, by = 3),
         Sensor2mean = rollapply(Sensor2, width = 3, FUN = median, align = "right", fill = NA, by = 3),
         Sensor3mean = rollapply(Sensor3, width = 3, FUN = median, align = "right", fill = NA, by = 3),
         Sensor4mean = rollapply(Sensor4, width = 3, FUN = median, align = "right", fill = NA, by = 3)) %>%
  select(datetime, MachineID, Sensor1mean, Sensor2mean, Sensor3mean, Sensor4mean) %>%
  filter(!is.na(Sensor1mean))%>% 
  ungroup()
  print("B")
```


##### Creating 4 Columns Sensor1sd,Sensor2sd,Sensor3sd,Sensor4sd out of available columns . Columns are derived by taking moving standard deviations of 3 records for every third record.
```{r}
OperCondDatasd <- OperCondData %>% 
  arrange(MachineID, datetime) %>%
  group_by(MachineID) %>%
  mutate(Sensor1sd = rollapply(Sensor1, width = 3, FUN = sd, align = "right", fill = NA, by = 3),
         Sensor2sd = rollapply(Sensor2, width = 3, FUN = sd, align = "right", fill = NA, by = 3),
         Sensor3sd = rollapply(Sensor3, width = 3, FUN = sd, align = "right", fill = NA, by = 3),
         Sensor4sd = rollapply(Sensor4, width = 3, FUN = sd, align = "right", fill = NA, by = 3)) %>%
  select(datetime, MachineID, Sensor1sd, Sensor2sd, Sensor3sd, Sensor4sd) %>%
  filter(!is.na(Sensor1sd)) %>%
  ungroup()

```

##### Creating 4 Columns Sensor1mean_24hrs,Sensor2mean_24hrs,Sensor3mean_24hrs,Sensor4mean_24hrs out of available columns . Columns are derived by taking moving means of 24 records for every third record.
```{r}
OperCondDatamean_24hrs <- OperCondData %>%
  arrange(MachineID, datetime) %>%
  group_by(MachineID) %>%
  mutate(Sensor1mean_24hrs = rollapply(Sensor1, width = 24, FUN = median, align = "right", fill = NA, by = 3),
         Sensor2mean_24hrs = rollapply(Sensor2, width = 24, FUN = median, align = "right", fill = NA, by = 3),
         Sensor3mean_24hrs = rollapply(Sensor3, width = 24, FUN = median, align = "right", fill = NA, by = 3),
         Sensor4mean_24hrs = rollapply(Sensor4, width = 24, FUN = median, align = "right", fill = NA, by = 3)) %>%
  select(datetime, MachineID, Sensor1mean_24hrs, Sensor2mean_24hrs, Sensor3mean_24hrs, Sensor4mean_24hrs) %>%
  filter(!is.na(Sensor1mean_24hrs)) %>% 
  ungroup()

```

##### Creating 4 Columns Sensor1sd_24hrs,Sensor2sd_24hrs,Sensor3sd_24hrs,Sensor4sd_24hrs out of available columns . Columns are derived by taking moving standard deviations of 24 records for every third record.
```{r}

OperCondDatasd_24hrs <- OperCondData %>% 
  arrange(MachineID, datetime) %>%
  group_by(MachineID) %>%
  mutate(Sensor1sd_24hrs = rollapply(Sensor1, width = 24, FUN = sd, align = "right", fill = NA, by = 3),
         Sensor2sd_24hrs = rollapply(Sensor2, width = 24, FUN = sd, align = "right", fill = NA, by = 3),
         Sensor3sd_24hrs = rollapply(Sensor3, width = 24, FUN = sd, align = "right", fill = NA, by = 3),
         Sensor4sd_24hrs = rollapply(Sensor4, width = 24, FUN = sd, align = "right", fill = NA, by = 3)) %>%
  select(datetime, MachineID, Sensor1sd_24hrs, Sensor2sd_24hrs, Sensor3sd_24hrs, Sensor4sd_24hrs) %>%
  filter(!is.na(Sensor1sd_24hrs)) %>%
  ungroup()

```

##### Creating a Data Frame OperCondDatafeat with all the features derived above.

```{r}
OperCondDatafeat <- data.frame(OperCondDatamean, OperCondDatasd[,-c(1:2)]) 
OperCondDatafeat_24hrs <- data.frame(OperCondDatamean_24hrs, OperCondDatasd_24hrs[,-c(1:2)])
OperCondDatafeat <- OperCondDatafeat %>%
  left_join(OperCondDatafeat_24hrs, by = c("datetime", "MachineID")) %>%
  filter(!is.na(Sensor1mean_24hrs)) %>% 
  ungroup()

```

##### There are 5 different error types in in Complaints Log file. Creating an integer column for each error type.

```{r}
# create a column for each error type
errorcount <- ComplaintsLog %>% select(datetime, MachineID, errorID) %>% 
  mutate(error1 = as.integer(errorID == "error1"), 
         error2 = as.integer(errorID == "error2"),
         error3 = as.integer(errorID == "error3"),
         error4 = as.integer(errorID == "error4"),
         error5 = as.integer(errorID == "error5"))
```

##### Adding all the errors of each type and getting 5 different features

```{r}
# sum the duplicate ComplaintsLog in an hour
errorcount <- errorcount %>% 
  group_by(MachineID,datetime)%>%
  summarise(error1sum = sum(error1), 
            error2sum = sum(error2), 
            error3sum = sum(error3), 
            error4sum = sum(error4), 
            error5sum = sum(error5)) %>%
  ungroup()

```

##### Merging the errors features derived above with Operating Condtions Data.
```{r}
errorfeat <- OperCondData %>% 
  select(datetime, MachineID) %>%
  left_join(errorcount, by = c("datetime", "MachineID"))

# replace missing values
errorfeat[is.na(errorfeat)] <- 0

```

##### Taking the count of all the 5 features derived that has the sum of count of each error type

```{r}
# count the number of ComplaintsLog of different types in the last 24 hours,  for every 3 hours
errorfeat <- errorfeat %>% 
  arrange(MachineID, datetime) %>%
  group_by(MachineID) %>%
  mutate(error1count = rollapply(error1sum, width = 24, FUN = sum, align = "right", fill = NA, by = 3),
         error2count = rollapply(error2sum, width = 24, FUN = sum, align = "right", fill = NA, by = 3),
         error3count = rollapply(error3sum, width = 24, FUN = sum, align = "right", fill = NA, by = 3),
         error4count = rollapply(error4sum, width = 24, FUN = sum, align = "right", fill = NA, by = 3),
         error5count = rollapply(error5sum, width = 24, FUN = sum, align = "right", fill = NA, by = 3)) %>%
  select(datetime, MachineID, error1count, error2count, error3count, error4count, error5count) %>%
  filter(!is.na(error1count)) %>% 
  ungroup()

```

##### Creating 4 features comp1,comp2,comp3,comp4 from Component Service Log data. one for every differnet Component Attended. There are 4 differnt ComponentAttended - Component1,Component2,Component3,Component4
```{r}
# create a binary column for each component. 1 if replacement occured, 0 if not.
compAttendedRep <- ComponentServiceLog %>% 
  select(datetime, MachineID, ComponentAttended) %>% 
  mutate(comp1 = as.integer(ComponentAttended == "Component1"), 
         comp2 = as.integer(ComponentAttended == "Component2"),
         comp3 = as.integer(ComponentAttended == "Component3"),
         comp4 = as.integer(ComponentAttended == "Component4")) %>%
  select(-ComponentAttended)


compAttendedRep <- as.data.table(compAttendedRep)
setkey(compAttendedRep, MachineID, datetime)

# seperate different component type replacements into different tables
comp1rep <- compAttendedRep[comp1 == 1, .(MachineID, datetime, lastrepcomp1 = datetime)]# component 1 replacements
comp2rep <- compAttendedRep[comp2 == 1, .(MachineID, datetime, lastrepcomp2 = datetime)]# component 2 replacements
comp3rep <- compAttendedRep[comp3 == 1, .(MachineID, datetime, lastrepcomp3 = datetime)]# component 3 replacements
comp4rep <- compAttendedRep[comp4 == 1, .(MachineID, datetime, lastrepcomp4 = datetime)]# component 4 replacements

# use OperCondData feature table datetime and MachineID to be matched with replacements
compdate <- as.data.table(OperCondDatafeat[,c(1:2)]) 
setkey(compdate, MachineID, datetime)

# data.table rolling match will attach the latest record from the component replacement tables 
# to the OperCondData date time and MachineID
comp1feat <- comp1rep[compdate[,.(MachineID, datetime)],roll = TRUE] 
comp1feat$sincelastcomp1 <- as.numeric(difftime(comp1feat$datetime, comp1feat$lastrepcomp1, units = "days"))
comp2feat <- comp2rep[compdate[,.(MachineID, datetime)], roll = TRUE] 
comp2feat$sincelastcomp2 <- as.numeric(difftime(comp2feat$datetime, comp2feat$lastrepcomp2, units = "days"))
comp3feat <- comp3rep[compdate[,.(MachineID, datetime)], roll = TRUE] 
comp3feat$sincelastcomp3 <- as.numeric(difftime(comp3feat$datetime, comp3feat$lastrepcomp3, units="days"))
comp4feat <- comp4rep[compdate[,.(MachineID, datetime)], roll = TRUE] 
comp4feat$sincelastcomp4 <- as.numeric(difftime(comp4feat$datetime, comp4feat$lastrepcomp4, units = "days"))

# merge all tables
compAttendedFeatures <-data.frame(compdate, comp1feat[,.(sincelastcomp1)], comp2feat[,.(sincelastcomp2)],
                      comp3feat[,.(sincelastcomp3)],comp4feat[,.(sincelastcomp4)])

```

##### Combining all the features to get finalfeatures to be used for Model Building.

```{r}
finalfeatures <- data.frame(OperCondDatafeat, errorfeat[,-c(1:2)])

# merge with component features and machine features lastly
finalfeatures <- finalfeatures %>% 
  left_join(compAttendedFeatures, by = c("datetime","MachineID")) %>% 
  left_join(MachinesDetails, by = c("MachineID"))

head(finalfeatures, 10)
cat("The final set of features are:",paste0(names(finalfeatures), ","))

```

```{r}
FinalFeatUniqueMID <-  as.data.frame(unique(finalfeatures$MachineID))
```

##### Transforming the final features data set to derived a single record for each Machine ID. Mean of values for each feature is taken for every Machine ID.
```{r}
FinalFeatTrain <- finalfeatures %>% group_by(MachineID) %>%
  mutate(NewSensor1men=median(Sensor1mean),NewSensor2mean = median(Sensor2mean),Newpressurmean = median(Sensor3mean),NewSensor4mean=median(Sensor4mean),NewSensor1sd = median(Sensor1sd),           
         NewSensor2sd=mean(Sensor2sd),NewSensor3sd = mean(Sensor3sd),NewSensor4sd = mean(Sensor4sd),NewSensor1mean_24hrs = mean(Sensor1mean_24hrs),   
         NewSensor2mean_24hrs = median(Sensor2mean_24hrs),NewSensor3mean_24hrs = median(Sensor3mean_24hrs),NewSensor4mean_24hrs = median(Sensor4mean_24hrs),
         NewSensor1sd_24hrs = mean(Sensor1sd_24hrs),NewSensor2sd_24hrs = mean(Sensor2sd_24hrs),NewSensor3sd_24hrs = mean(Sensor3sd_24hrs),NewSensor4sd_24hrs = median(Sensor4sd_24hrs),  
         Newerror1count = mean(error1count),Newerror2count = mean(error2count),Newerror3count = mean(error3count),Newerror4count = mean(error4count),        
         Newerror5count = median(error5count),Newsincelastcomp1 = median(sincelastcomp1),Newsincelastcomp2 = median(sincelastcomp2),Newsincelastcomp3 = median(sincelastcomp3),     
         Newsincelastcomp4 = median(sincelastcomp4),     
         NewServicePeriod = mean(ServicePeriod)) %>%
   select (MachineID,NewSensor1men,NewSensor2mean,Newpressurmean,NewSensor4mean,NewSensor1sd,NewSensor2sd,NewSensor3sd,       
           NewSensor4sd,NewSensor1mean_24hrs,NewSensor2mean_24hrs,NewSensor3mean_24hrs,NewSensor4mean_24hrs,NewSensor1sd_24hrs,
           NewSensor2sd_24hrs,NewSensor3sd_24hrs,NewSensor4sd_24hrs,Newerror1count,Newerror2count,Newerror3count,Newerror4count,        
           Newerror5count,Newsincelastcomp1,Newsincelastcomp2,Newsincelastcomp3,Newsincelastcomp4,NewServicePeriod)

DistinctFinalFeatTrain <- distinct(FinalFeatTrain)
```

##### Reading the Train and Test Data.
```{r}
train <- read.csv("C:\\Users\\SaiRam\\Desktop\\PHD\\phd_dataFinal\\Train.csv",header = TRUE)
test <- read.csv("C:\\Users\\SaiRam\\Desktop\\PHD\\phd_dataFinal\\Test.csv",header = TRUE)

```

##### Joining Train Data with the Final Features to get all the required features for every MachineID.
```{r}
NewTrain <- train %>% 
  left_join(DistinctFinalFeatTrain, by = c("MachineID","MachineID")) %>% 
  left_join(MachinesDetails, by = c("MachineID"))
nrow(NewTrain)
NewTrain$MachineID <- NULL
NewTrain$model <- NULL
NewTest <- test %>%
  left_join(DistinctFinalFeatTrain, by = c("MachineID","MachineID")) %>% 
  left_join(MachinesDetails, by = c("MachineID"))
NewTest$MachineID <- NULL
NewTest$model <- NULL
```

##### Target Column ActionPoint is converted to Factor

```{r}
levels(NewTrain$ActionPoint) <- c(levels(NewTrain$ActionPoint), "none")
NewTrain$ActionPoint[is.na(NewTrain$ActionPoint)]<-"none"
```

##### Model Building using Gradient Boosting.
```{r}
gbm_model11 <- gbm(formula = ActionPoint~., data = NewTrain, 
                  distribution = "multinomial", n.trees = 50,
                  interaction.depth = 5, shrinkage = 0.1)

summary(gbm_model11)
```

##### Predicting on Train Data Set

```{r}
pred_gbm11 <- as.data.frame(predict(gbm_model11, NewTrain, n.trees = 50,type = "response"))

names(pred_gbm11) <- gsub(".50", "", names(pred_gbm11))
pred_gbm11$ActionPoint <- as.factor(colnames(pred_gbm11)[max.col(pred_gbm11)])
```

##### Predicting on Test Data Set

```{r}
pred_gbm12 <- as.data.frame(predict(gbm_model11, NewTest, n.trees = 50,type = "response"))
names(pred_gbm12) <- gsub(".50", "", names(pred_gbm12))
pred_gbm12$ActionPoint <- as.factor(colnames(pred_gbm12)[max.col(pred_gbm12)])
```

##### Creating the Submission File.

```{r}
NewDF <- data.frame("MachineID"=test$MachineID,"ActionPoint"=pred_gbm12$ActionPoint)
write.csv(NewDF,"Submission21.csv")


```

```{r}

gbm_modelNew <- gbm(formula = ActionPoint~Newsincelastcomp3+Newerror3count+NewSensor2sd+Newsincelastcomp4+NewSensor4sd_24hrs+Newsincelastcomp2+NewSensor4mean+NewSensor4mean_24hrs+NewSensor2mean+NewSensor3sd_24hrs+NewSensor3sd+Newpressurmean+Newsincelastcomp1+NewServicePeriod+NewSensor1men+NewSensor4sd+NewSensor2mean_24hrs+NewSensor1sd_24hrs+NewSensor1sd+Newerror1count+NewSensor2sd_24hrs+NewSensor3mean_24hrs+Newerror2count, data = NewTrain, 
                  distribution = "multinomial", n.trees = 50,
                  interaction.depth = 5, shrinkage = 0.1)

summary(gbm_modelNew)                                          

```

```{r}

pred_gbmNew <- as.data.frame(predict(gbm_modelNew, NewTest, n.trees = 50,type = "response"))
names(pred_gbmNew) <- gsub(".50", "", names(pred_gbmNew))
pred_gbmNew$ActionPoint <- as.factor(colnames(pred_gbmNew)[max.col(pred_gbmNew)])

NewDF <- data.frame("MachineID"=test$MachineID,"ActionPoint"=pred_gbm12$ActionPoint)
write.csv(NewDF,"Submission2.csv")
```





```{r}
gbm_modelNew <- gbm(formula = ActionPoint~Newerror3count+Newerror1count+Newerror2count+Newerror4count, data = NewTrain, 
                  distribution = "multinomial", n.trees = 50,
                  interaction.depth = 5, shrinkage = 0.1)

summary(gbm_modelNew)
pred_gbmNew <- as.data.frame(predict(gbm_modelNew, NewTest, n.trees = 50,type = "response"))
names(pred_gbmNew) <- gsub(".30", "", names(pred_gbmNew))
pred_gbmNew$ActionPoint <- as.factor(colnames(pred_gbmNew)[max.col(pred_gbmNew)])
NewDF <- data.frame("MachineID"=test$MachineID,"ActionPoint"=pred_gbm12$ActionPoint)
write.csv(NewDF,"Submission3.csv")

```
